%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% %---------------------------------------------------------
%   \cventry
%     {Founding Member \& Site Reliability Engineer \& Infrastructure Team Lead} % Job title
%     {Danggeun Pay Inc. (KarrotPay)} % Organization
%     {Seoul, S.Korea} % Location
%     {Mar. 2021 - Jun. 2023} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Everything that matters.}
%         \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
%         \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)}
%         \item {Established a standardized base for declarative management of infrastructures and service deployments, enabling operational efficiency and consistency. Over 90\% of AWS resources were all managed through standardized terraform modules. All add-ons and service workloads on the Kubernetes cluster were managed on a GitOps basis with Kustomize and ArgoCD.}
%         \item {Saved over 30\% of the overall AWS costs by establishing a quarterly purchasing strategiy for RI (Reserved Instance) and SP (Savings Plan) and by introducing Graviton instances.}
%         \item {Established a core architecture for regulating of outbound DNS traffic in multi-account and multi-VPC environments utilizing AWS Route53 DNS Firewall and FMS. This significantly increased the level of security confidence in the financial sector's segregated environment.}
%         \item {Introduced Okta employee identity solution in the company, establishing security policies and configuring SSO integration with over 20 enterprise systems including AWS, GitHub, Slack, Google Workspace. Set up a Hub and Spoke architecture, enabling a collaborative account structure with the parent company, Daangn Market.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
\cventry
  {Senior Software Development Engineer} % Job title
  {Amazon Web Services (AWS)} % Organization
  {Greater Seattle Area, USA} % Location
  {Jun. 2022 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and enhanced new DynamoDB storage engine}
      \item {We built some very cool replication technology that backs both DynamoDB Strongly Consistent Global Tables and Aurora DSQL's multi-region mode.}
      \item {Mentored teams on Rust programming and guided efforts to adopt new methodologies for software development.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Senior Software Engineer} % Job title
  {Google} % Organization
  {USA} % Location
  {Nov. 2021 - Jun. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked on ChromeOS core virtualization technologies. Mostly crosvm - ChromeOS's VMM}
      \item {Open source Linux Kernel contributions to support ChromeOS virtualization solutions}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Senior Software Engineer} % Job title
  {Amazon, Project Kuiper} % Organization
  {Greater Seattle Area, USA} % Location
  {Nov. 2020 - Nov. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Owned the customer terminal dataplane, enhancing functionality and performance.}
      \item {Developed bootrom for a custom Project Kuiper ASIC}
      \item {Worked on automated processeses to simplify collaboration between hardware design and software teams}
      \item {Introduced the team to Rust programming and contributed to cross-functional projects outside of SDN area.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Software Development Engineer} % Job title
  {Amazon Web Services (AWS), DynamoDB} % Organization
  {Greater Seattle Area, USA} % Location
  {Apr. 2017 - Oct. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led multiple projects to improve encryption, storage costs, and performance in a storage engine layer}
      \item {Designed and implemented algorithms for distributed admission control}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Software Development Engineer} % Job title
  {Amazon Web Services (AWS), Edge Services} % Organization
  {Greater Seattle Area, USA} % Location
  {Oct. 2013 - Apr. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and delivered multiple features in internal DPDK-based AntiDDOS complex}
      \item {Contributed to the development of AWS Shield and Anti-DDoS solutions.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Senior Engineer, Project Lead} % Job title
  {Samsung Electronics Ukraine R\&D} % Organization
  {Kyiv, Ukraine} % Location
  {Feb. 2011 - Sep. 2013} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led research and development of security and middleware solutions for Samsung Electronics products.}
      \item {Developed and optimized embedded software for ARM-based systems using C/C++ and NEON.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Software Engineer} % Job title
  {ЛІГА} % Organization
  {Kyiv, Ukraine} % Location
  {Sep. 2007 - Feb. 2011} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and optimized software for Digital Rights Management (DRM) systems.}
      \item {Worked on natural language processing (NLP) projects to improve data analysis capabilities.}
      \item {Enhanced big data processing pipelines and implemented performance optimizations.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Systems/Software Engineer} % Job title
  {UkrCard JSC} % Organization
  {Kyiv, Ukraine} % Location
  {Jul. 2006 - Aug. 2007} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed cryptographic solutions and internal tools for secure financial transactions.}
      \item {Worked with HP NonStop Tandem Computers (Guardian/OSS) to ensure reliable systems performance.}
      \item {Implemented secure processing solutions using HP Atalla Network Security Processor.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Software Application Engineer} % Job title
  {Information Center for Personal Accounting System of Pension Fund of Ukraine} % Organization
  {Ukraine} % Location
  {2004 - 2006} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed software solutions using Oracle PL-SQL}
      \item {Programmed in Delphi and C/C++ for both Windows and Linux platforms.}
      \item {Streamlined processes for personal accounting systems to enhance operational efficiency.}
    \end{cvitems}
  } 

%---------------------------------------------------------
\end{cventries}
